Use of asynchronous circuits and leakiness in modeling biological circuit of the Caulobacter Crescentus cell cycle

### 2017-03-08 asyncleakyn.tex
added sr latch and c-element

For holds we want a minimum bound on the time the output remains within the '0' or '1' regions as the inputs are changed.  We first look at how long a signal stays in the '0' region, or hold 0 case.  We assume that the output eventually rises from the initial '0' value so that $z_{ss}>z_0$.  Note that if $z_{ss}<fanout_0$ then the output signal will be held at '0' indefinitely.  So we look at the case where $z_{ss}>fanout_0$.  Similar to finding the set time, we use the second form of the time equation.  This time we would like to find the minimum value for the time.  Since $\Delta t$ is monotonically increasing in $z_f$ and monotonically decreasing in $z_0$, we want to use the minimum $z_f$ such that the output stops being a valid '0' signal, that is $fanout_0$, and use the maximum $z_0$ that is a valid input '0', that is $g(in_{max0})$.  Additionally since the derivative of this equation with respect to $z_{ss}$ is always negative, we apply the largest possible 'hold' input where both active production and degradation are still considered '0'.  That is the baseline degradation and $in_{max0}$.  Because the degradation is different, the value $z_{ss}$ differs from $g(in_{max0})$, the input output pair has a different transfer function, call it $g'()$ so that the steady state output is $g'(in_{max0})$

@@

The analysis is similar for the minimum time a signal stays in the '1' region, or hold 1 case.  For this case the output eventually decays from the initial '1' value so $z_{ss}<z_0$. Again, if $z_{ss}>fanout_1$ then the output signal will be held at '1' indefinitely. So we look at the case where $z_{ss}<fanout_1$.  Similar to finding the reset time, we use the first form of the time equation.   We would like to find the minimum value for the time.  Since $\Delta t$ is monotonically decreasing in $z_f$ and monotonically increasing in $z_0$, we want to use the maximum $z_f$ such that the output stops being a valid '1' signal, that is $fanout_1$, and use the minimum $z_0$ that is a valid input '1', that is $g(in_{min1})$.  Additionally since the derivative of this equation with respect to $z_{ss}$ is always positive, we apply the smallest possible 'hold' input where both active production and degradation are still considered '0'.  That is the baseline degradation and $in_{min0}$.  Again due to the difference in degradation rate, we use a different input output transfer function $g'()$ so that the steady state output is $g'(in_{min0})$  

>>>>

For holds we want a minimum bound on the time the output remains within the '0' or '1' regions as the inputs are changed.  We first look at how long a signal stays in the '0' region, or the hold 0 case.  We assume that the output eventually rises from the initial '0' value so that $z_{ss}>z_0$.  Note that if $z_{ss}<fanout_0$ then the output signal will be held at '0' indefinitely.  So we look at the case where $z_{ss}>fanout_0$.  Similar to finding the set time, we use the second form of the time equation.  This time we would like to find the minimum value for the time.  Since $\Delta t$ is monotonically increasing in $z_f$ and monotonically decreasing in $z_0$, we want to use the minimum $z_f$ such that the output stops being a valid '0' signal, that is $fanout_0$, and use the maximum $z_0$ that is a valid input '0', that is $g(in_{max0})$.  Additionally since the derivative of this equation with respect to $z_{ss}$ is always negative, we apply the largest possible 'hold' input where both active production and degradation are still considered '0'.  That is the baseline degradation and $in_{max0}$.  Because the degradation is different, the value $z_{ss}$ differs from $g(in_{max0})$, the input output pair has a different transfer function, call it $g'()$ so that the steady state output is $g'(in_{max0})$

@@

The analysis is similar for the minimum time a signal stays in the '1' region, or the hold 1 case.  For this case the output eventually decays from the initial '1' value so $z_{ss}<z_0$. Again, if $z_{ss}>fanout_1$ then the output signal will be held at '1' indefinitely. So we look at the case where $z_{ss}<fanout_1$.  Similar to finding the reset time, we use the first form of the time equation.   We would like to find the minimum value for the time.  Since $\Delta t$ is monotonically decreasing in $z_f$ and monotonically increasing in $z_0$, we want to use the maximum $z_f$ such that the output stops being a valid '1' signal, that is $fanout_1$, and use the minimum $z_0$ that is a valid input '1', that is $g(in_{min1})$.  Additionally since the derivative of this equation with respect to $z_{ss}$ is always positive, we apply the smallest possible 'hold' input where both active production and degradation are still considered '0'.  That is the baseline degradation and $in_{min0}$.  Again due to the difference in degradation rate, we use a different input output transfer function $g'()$ so that the steady state output is $g'(in_{min0})$  
